---
title: 'Mermaid '
author: Package Build
date: '2024-02-08'
slug: []
categories:
  - Programming
tags:
  - Programming
type: ''
subtitle: ''
image: ''
---

I was told by a JD Long at a recent conference where I brought up Code2Flow that Mermaid could be used just like Code2Flow within R/Github/etc to draw flowcharts, but it also has other functions that makes it a more generally useful program. Thanks James! 

Mermaid is also accessible within R Studio so I can try it here.

[Mermaid Live Editor](https://mermaid.live/edit#)

# Simple Mermaid diagram

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In R Studio, DiagrammeR would be the package to install for producing Mermaid graphics.

```{r}
library(DiagrammeR)
mermaid("
graph LR
    A-->B
    ")
```

#Gantt Chart

```{r}
mermaid("
gantt
    title A Gantt Diagram
    dateFormat  YYYY-MM-DD
    section Section
    A task           :a1, 2014-01-01, 30d
    Another task     :after a1  , 20d
    section Another
    Task in sec      :2014-01-12  , 12d
    another task      : 24d",
    height = '100%', width = '100%'
)
```

#Flowchart but called Graph in the R package.

```{r}
mermaid("

graph TD
    A[Christmas] -->|Get money| B(Go shopping)
    B --> C{Let me think}
    C -->|One| D[Laptop]
    C -->|Two| E[iPhone]
    C -->|Three| F[fa:fa-car Car]"
)
```
